%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------
\cventry
{CCIM Modernization Program Manager, GS-1701-11/*GS-301-12} % Job title
{Defense Language Institute English Language Center} % Organization
{San Antonio, TX} % Location
{JUL 2022 - PRESENT, 40 hrs/wk} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {*Currently awaiting reclassification of position}
\item {Active Secret Clearance, Top Secret with SCI in progress.}
\item {Track and report status for 45 concurrent projects in modernization efforts related to technology, infrastructure, academics and training.}
\item {Coordinate and attend weekly sync meetings with stakeholders/POCs across the 37 Training Wing.}
\item {Prepare weekly briefings for Commander staff meeting.}
\item {Build and maintain local external partnerships for DLIELC.}
\item {Built out tracking system and identified short-falls of current software to write justification for project management software to aid in tracking, reporting and data visualization.} 
\end{cvitems}
}

%------------------------------------------------
\cventry
{ESL/EFL Instructor, GS-1701-11} % Job title
{Defense Language Institute English Language Center} % Organization
{San Antonio, TX} % Location
{AUG 2020 - JULY 2022, 40 hrs/wk} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Represented 332 Training Squadron by participating in the DoD BRAVO 1 Hackathon at Langley AFB, which sought to better understand and use AF data in support of innovation and change.}
%\item {Detailed to the CCIM Modernization Team as project manager.} 
\item {Team lead for 6-month Mobile Training Team in Riyadh, Saudi Arabia.}
\item {Coordinated with US Army SCO, Saudi military leaders and Navy SEAL program instructors to accomplish English language mission goals.}
\item {Assisted in preparing for validation project of American Language Course Level 0 in Riyadh, KSA.}
%\item {Taught beginning level English courses for Saudi Special Forces.}
%\item {Teach English courses for joint force program between US Army, US Air Force and foreign military partners.}
\item {Teach English courses for US Armed Forces to prepare foreign military partners for follow on trainings in CONUS, online and in-person.}
\item {Administered and proctor ECL and ALCPT examinations.}
\item {Coordinated student and teacher course schedules.}
\item {Track and report student progress for attendance and assessments.}
\item {Built Google Forms and Scripts to support data collection, tracking and reporting for DLI professional development conference.}
\item {Provided technical support to colleagues and managed weekly assessments for Levels 1-5 in General English with the Distance Learning Support Team.}
\item {Conducted telework training for instructors on integrating technology in the classroom.}
\item {Plan, organize and implement weekly lesson plans for ALC books.}
\item {Cultivate a positive student-centered learning environment where students used language to complete tasks rather than just complete drills or rote memorization.}
\item {Provide students with error correction and feedback for grammar, vocabulary and pronunciation that cause communication breakdowns.}
%\item {Responsible for completion of administrative tasks related to teaching, training and status reporting.} 
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Spanish Basic Language Program Coordinator} % Job title
{University of Arizona} % Organization
{Tucson, AZ} % Location
%{AUG 2016 - MAY 2021} % Date(s)
{AUG 2017 - MAY 2021, 20 hrs/wk} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Designed and tracked Spanish Basic Language Coordination Team (BLP) program evaluation assessments using Taskstream.}
\item {Assisted in transitioning 107 Spanish courses to online formats with no lost instruction time in response to the COVID-19 pandemic.}
\item {Trained and supported the 6 members of the BLP coordination team.}
\item {Created video trainings to complement 1-on-1 training of my replacement for sustainability of programatic admin processes.}
\item {Built and managed 27 course sites using D2L as the learning management system per semester.}
\item {Built and maintained D2L development sites containing course materials, question banks and assessments.}
\item {Wrote and aligned Spanish course goals and objectives with ACTFL guidelines and Quality Matters standards.}
\item {Created RScripts to generate dynamic reports in order to revise and maintaine 27 individual syllabi for Spanish BLP.}
\item {Served as lead coordinator in course design and new textbook adoption for Spanish 101, 102, and 251}
\item {Created new rubrics in conjunction with the Office of Instruction and Assessment.}
\item {Provided teaching and technical support for Spanish program---approximately 70 instructors and 3500 students per semester.}
\item {Served as Vista Higher Learning Faculty Specialist for the Department of Spanish and Portuguese.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Spanish Instructor} % Job title
{University of Arizona} % Organization
{Tucson, AZ} % Location
%{AUG 2016 - MAY 2021} % Date(s)
{AUG 2016 - MAY 2020, 20 hrs/wk} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Taught beginner and intermediate Spanish courses through face-to-face, hybrid, remote-learning and online formats.}
\item {Taught undergraduate level Applied Linguistics,Spanish/Linguistics 457 focusing on foreign language methodologies and technology in the classroom.} 
\item {Piloted Spanish 101 course for new online platform, MindTAP, per request of Cengage publishing company.}
\end{cvitems}
}

%------------------------------------------------ 
\cventry
{English as Second Language Instructor} % Job title
{West Virginia University} % Organization
{Morgantown, WV} % Location
%{JAN 2013 - MAY 2016} % Date(s)
{JAN 2013 - MAY 2016, 30 hrs/wk} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Designed and implemented a two-course technology-based elective series.}
\item {Coordinated the English Conversation Partner Program.}
\item {Taught beginner through advanced levels English classes.}
\item {Prepared documentation for Commission on English Language Accreditation.}
\item {Certified as SPEAK test grader used for international instructors' ability to teach in English speaking universities.}
\item {Administered and proctored Michigan Placement Exams and Institutional paper-based TOEFL exam.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Owner} % Job title
{Asberry Landscapes, LLC} % Organization
{Morgantown, WV} % Location
%{JAN 2012 - DEC 2014} % Date(s)
{JAN 2012 - DEC 2014, 60 hrs/wk} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Trained crew members on instrumentation and best practices in field surveying for oil and gas industry.}
\item {Organized and delegated field work to appropriate survey crew members.}
\item {Documented pipeline survey field work completed by survey crews.}
\item {Submitted final field reports to project manager and engineering drafters.} 
\end{cvitems} 
}

%------------------------------------------------

\cventry
{GIS Technician II} % Job title
{EQT Midstream} % Organization
{Clarksburg, WV \& Waynesburg, PA} % Location
%{MAR 2010 - OCT 2012} % Date(s)
{MAR 2010 - OCT 2012, 40 hrs/wk} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Produced updated maps in ESRI and print maps for field staff.}
\item {Managed company asset database in ESRI and integration of field work ticket system.}
\item {Trained newly hired GIS Technicians on company ESRI servers.}
\item {Trained pipeliners, field staff, on high precision GPS equipment.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{AmeriCorps VISTA Volunteer} % Job title
{Upper Tennessee River Roundtable} % Organization
{Tazewell, VA} % Location
%{OCT 2009 - MAR 2010} % Date(s)
{OCT 2009 - MAR 2010, 40 hrs/wk} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Provided educational resources and classes for local schools and clubs.}
\item {Volunteered in community engagement events to help raise funds for local Southwest Virginian charities.}
\item {Met with landowners interested in making their farming practices more sustainable while protecting riparian zones on their land.}
\item {Maintained professional relationships with government and university agencies to support NGO mission.}
\item {Worked with colleagues on grant writing used for on-going organizational support.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Research Assistant} % Job title
{Hydrogeology Research Center} % Organization
{Morgantown, WV} % Location
%{AUG 2008 - MAY 2009} % Date(s)
{AUG 2008 - MAY 2009, 20 hrs/wk} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Maintained community and government relationships for Ruth Bell restoration project.}
\item {Created online maps in ArcIMS.}
\item {Managed ESRI water quality database.}
\item {Collected water samples and appended data to the ESRI water quality database.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{AmeriCorps VISTA Volunteer} % Job title
{Friends of Cheat} % Organization
{Kingwood, WV} % Location
%{AUG 2007 - AUG 2008} % Date(s)
{AUG 2007 - AUG 2008, 40 hrs/wk} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Taught GIS workshops at AmeriCorps VISTA Training.}
\item {Presented results extracted from GIS reports.}
\item {Maintained ArcGIS database of water samples.}
\item {Provided educational resources and classes for local schools and clubs.}
\item {Attended board meetings for the Outdoor Education Classroom Committee.}
\item {Led community outreach initiative through volunteer recruitment and land owner negotiations.}
\item {Maintained professional relationships with government and university agencies to support NGO mission.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Research Assistant} % Job title
{National Geospatial Development Center} % Organization
{Morgantown, WV} % Location
%{SEP 2006 - AUG 2007} % Date(s)
{SEP 2006 - AUG 2007, 20 hrs/wk} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed soils-related educational posters with ArcGIS.}
\item {Redesigned educational website to ensure user friendliness.}
\item {Restored and prepared historical soil surveys for posting on the USDA Natural Resource Conservation Services website.}
\item {Developed AutoCAD drawings for machinist to construct water infiltration simulation display.}
\end{cvitems}
}

%------------------------------------------------
\vspace{-3mm}
\end{cventries}