%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Service}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------
\cventry
{Instructor/Maintainer} % Affiliation/role
{Software Carpentries} % Organization/group
{Online} % Location
{2019 - Present} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Certified carpentries instructor.}
\item {Serve as carpentries maintainer for geospatial lesson, Introduction to Geospatial Raster and Vector Data with R.}
\item {Taught in-person workshop to ~50 University of Arizona students, staff and faculty in February 2020. Content included: Introduction to UNIX shell, git and using GitHub and Introduction to Python using Jupyter Notebooks.}
\item {Served as a helper for carpentries workshop for ~50 researchers in October 2019.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Faculty Specialist} % Affiliation/role
{VISTA Higher Learning} % Organization/group
{Tucson, AZ} % Location
{2018 - 2021} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Provided University of Arizona campus support as local representative for VISTA online learning services/portals.}
\item {Led training workshops for graduate students, instructors and lecturers in Spanish.}
\end{cvitems}
}

%------------------------------------------------
\cventry
{Instructor} % Affiliation/role
{RezBaz Arizona 2021} % Organization/group
{University of Arizona, via Zoom} % Location
{17 MAY 2021} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Invited to present at the annual RezBaz conference.}
\item {Taught 4-hour online workshop using Jupyter Notebooks and Binder called Introduction to Python.}
\end{cvitems}
}

%------------------------------------------------
\cventry
{Instructor/Planner} % Affiliation/role
{RezBaz Arizona 2020} % Organization/group
{University of Arizona, via Zoom} % Location
{18 MAY 2020 - 29 MAY 2020} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Served on conference planning committee, which provided ~250 researchers with hands-on instruction.}
\item {Co-taught pre-conference session for instructors on how to use Zoom as a teaching platform.}
\item {Taught Introduction to Python using Jupyter Notebooks via Binder.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Data Science Ambassador} % Affiliation/role
{College of Humanities, University of Arizona} % Organization/group
{Tucson, AZ} % Location
{AUG 2019 - MAY 2020} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Addressed questions related to data science through consultations, training, and/or referrals to resources and experts (on-campus or online).}
\item {Developed training material for data science as it relates to the humanities.}
\item {Provided support at weekly events where researchers came with questions about their own data and/or processes.}
\end{cvitems}
}

%------------------------------------------------
\cventry
{Instructor} % Affiliation/role
{Cyber Carpentry} % Organization/group
{University of North Carolina} % Location
{14 JUL 2019 - 28 JUL 2019} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Provided instructional help and expertise at workshop for graduate students and post-docs from a variety of disciplines with an interest in reproducible science.}
\item {Led group of participants from workshop in an effort to develop material that can be used as reference material for themselves as well as their collaborators.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Webmaster} % Affiliation/role
{SLATSA  (Second Language Acquisition and Teaching Student Association)} % Organization/group
{Tucson, AZ} % Location
{2018 - 2019} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Built and maintained the annual conference website.}
\item {Set up university organization email accounts and maintained SLATSA listserv.}
\end{cvitems}
}

%------------------------------------------------

%\cventry
%{Analysis Representative} % Affiliation/role
%{SLATSA } % Organization/group
%{Tucson, AZ} % Location
%{2017 - 2018} % Date(s)
%{ % Description(s) of experience/contributions/knowledge
%\begin{cvitems}
%\item {Reviewed journal submissions for Arizona Working Papers.}
%\item {Advised students interested in taking classes related to language analysis.}
%\end{cvitems}
%}

%------------------------------------------------

\end{cventries}